\documentclass[11pt]{article}

% ==========  PACKAGE SETUP  ==========
\usepackage[margin=1in,top=0.5in]{geometry} % top margin 改小
\usepackage[T1]{fontenc}
\usepackage{lmodern}               
\usepackage{amsmath,amssymb}
\usepackage{enumitem}              % 控制列表外观
\usepackage{titlesec}              % 自定义标题格式
\usepackage{fancyhdr}              % 页眉/页脚 (如果需要)
\usepackage{setspace}              % 行距控制 (可选)

% 不要页码
\pagestyle{empty}

\begin{document}

% ========== HEADER (NAME + ADDRESS + CONTACT) ==========
\begin{center}
    {\large \textbf{JIAWEI WENG}}\\  % 你的名字
    3723 Oleander Ter, West Palm Beach, FL 33404 \\
    (917)-244-4903 \(\cdot\) EAD card \(\cdot\) \texttt{weng13860@gmail.com}
\end{center}

% ========== OBJECTIVE ==========
\section*{Objective}  
\vspace{-1.0em}
\hrule
\vspace{0.5em}

Seeking a full-stack Software Development Engineer full-time position, where I can leverage my experience in front-end and back-end development to build scalable applications and deliver high-quality user experiences.

% ========== EDUCATION ==========
\section*{Education}
\vspace{-1.0em}
\hrule
\vspace{0.5em}

\textbf{University of Florida, FL} \hfill 2021 -- 2025\\
\textit{B.S. in Computer Science}

% ========== TECHNICAL STRENGTHS ==========
\section*{Technical Strengths}
\vspace{-1.0em}
\hrule
\vspace{0.5em}

\begin{tabular}{@{} l p{12cm}}
\textbf{Computer Languages} & C++, C, Java, Python, SQL, TypeScript \\
\textbf{Frameworks}         & React, Node.js,Next.js \\
\textbf{Tools}              & Git, Clerk, Google Cloud Platform, Supabase, Prisma (ORM), Docker, MongoDB, RESTful API \\
\end{tabular}

% ========== COURSE PROJECT ==========
\section*{Course Project}
\vspace{-1.0em}
\hrule
\vspace{0.5em}

% 外层 itemize: 每个项目一个 \item，保证标题左对齐
\begin{itemize}[leftmargin=0pt, label={}, itemsep=0pt,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt]  % label={} 去掉外层黑点
  % --- Project 1: Cache Simulator ---
  \item 
    \textbf{Cache Simulator} \,|\, \textit{Simulation Program} \,|\, 2023
    \begin{itemize}[label=\textbullet, leftmargin=1.5em, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
      \item Developed a cache simulator using C++ to read a memory access trace from a file, 
            determine whether each memory access is a hit or a miss, and calculate the overall hit rate.
      \item It simulates different main memory and cache sizes, cache associativity
            (direct mapped, n-way associative, fully associative), and replacement methods (LRU, FIFO).
    \end{itemize}

  

  % --- Project 2: Custom Binary Search Tree ---
  \item
    \textbf{Custom Binary Search Tree} \,|\, \textit{Data Structure Program} \,|\, 2022
    \begin{itemize}[label=\textbullet, leftmargin=1.5em, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
      \item Created a custom BST using C++ that can store student names and IDs, providing 
            operations to add, remove, and search students in the tree.
      \item Supports printing student data in different traversals (in-order, pre-order, post-order),
            allowing easy organization and retrieval based on IDs.
    \end{itemize}

  

 

\end{itemize}

% ========== SIDE PROJECT ==========
\section*{Side Project}
\vspace{-1.0em}
\hrule
\vspace{0.5em}

\begin{itemize}[leftmargin=0pt, label={}, itemsep=0pt,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt]  % label={} 去掉外层黑点
  % --- Project 1: Cache Simulator ---
  \item 
    \textbf{AIDE} \,|\, \textit{Full-Stack Developer } \,|\, 
 September 2024 -- Present
    \begin{itemize}[label=\textbullet, leftmargin=1.5em, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item {User Authentication:} Integrated Clerk for secure sign-ups, logins, and session management, handling identity verification seamlessly.
  \item {RESTful APIs and AI Services:} Built a front-end/back-end data flow via RESTful APIs, utilizing third-party LLM endpoints for advanced AI responses. Introduced a \emph{tool call} mechanism (e.g., real-time weather, calculator) to ensure more accurate, context-aware outputs.
  \item {Data Persistence:} Employed Supabase (PostgreSQL + Prisma) to store user conversation content and manage version control. This setup maintains robust data integrity while simplifying schema migrations.
  \item {Editing Lock for Collaboration:} Implemented a lightweight concurrency lock so that once a user is editing a piece of content, others must wait until it’s released—preventing overwrite conflicts and ensuring consistent versioning.
\end{itemize}
\end{itemize}


\end{document}
